### 2024-01-27 tesis_Ashish/Chapter1/chapter1.tex
update 27 Jan 2024

During the operation of the CMS experiment, two main data-taking periods were conducted: Run 1, which spanned from 2010 to 2013, and Run 2, which took place from 2015 to 2018. During these periods, the CMS experiment measured the instantaneous and integrated luminosity of the proton-proton collisions produced by the LHC where the integrated luminosity for each year is shown in Fig.~\ref{fig:lumi}. During Run 1, the CMS experiment achieved a peak instantaneous luminosity of up to $5 \times 10^{33} cm^{-2} s^{-1}$, while during Run 2, the luminosity reached a peak value of up to $2 \times 10^{34} cm^{-2} s^{-1}$. The luminosity measurements during both runs were accompanied by careful assessments of the systematic uncertainties to ensure accurate and reliable results \cite{CMS-PAS-EWK-10-004, CMS-PAS-EWK-11-001, CMS-PAS-SMP-12-008, CMS-PAS-LUM-13-001, Sirunyan:2759951, pas_17, pas_18} as shown in Table. \ref{tab:lumi}.

>>>>

During the operation of the CMS experiment, two main data-taking periods were conducted: Run 1, which spanned from 2010 to 2013, and Run 2, which took place from 2015 to 2018. During these periods, the CMS experiment measured the instantaneous and integrated luminosity of the proton-proton collisions produced by the LHC where the integrated luminosity for each year is shown in Fig.~\ref{fig:lumi}. During Run 1, the CMS experiment achieved a peak instantaneous luminosity of up to $7.6 \times 10^{33} cm^{-2} s^{-1}$, while during Run 2, the luminosity reached a peak value of up to $2.1 \times 10^{34} cm^{-2} s^{-1}$. The luminosity measurements during both runs were accompanied by careful assessments of the systematic uncertainties to ensure accurate and reliable results \cite{CMS-PAS-EWK-10-004, CMS-PAS-EWK-11-001, CMS-PAS-SMP-12-008, CMS-PAS-LUM-13-001, Sirunyan:2759951, pas_17, pas_18} as shown in Table. \ref{tab:lumi}.

### 2024-01-27 tesis_Ashish/Chapter2/chapter2.tex
update 27 Jan 2024

\item Fast Beam Conditions Monitor (BCM1F) : The BCM1F is specifically designed to detect the ionization produced by charged particles passing through its diamond sensors, and to convert this signal into a measurement of the beam intensity and luminosity. The BCM1F consists of 24 diamond sensors, each with an active area of 1 cm², arranged in six rings around the beam pipe. The diamond sensors are positioned very close to the CMS detector, just 10 cm away from the beam pipe. This allows the sensors to detect the charged particles produced by the proton-proton collisions. When charged particles pass through the diamond sensors, they ionize the carbon atoms in the diamond crystal, producing electrons and holes. The electrons and holes are then collected by metal electrodes embedded in the diamond, producing a voltage signal proportional to the ionization produced by the charged particles. The voltage signal is then amplified by fast electronics and converted into a digital signal, which is sent to the CMS data acquisition system for further analysis. To measure the luminosity, the BCM1F counts the number of charged particles passing through each diamond sensor per unit time. The signal from each sensor is integrated over a short time interval (usually 25 ns), corresponding to the time it takes for a single proton bunch to pass through the sensors. The integrated signal is then converted into a measure of the instantaneous luminosity, which is proportional to the product of the number of charged particles per bunch and the collision frequency.

@@

\item Hadron Forward Calorimeter: The Hadron Forward (HF) Calorimeter is a critical component of the CMS experiment. It is a subdetector that measures the energy, position and arrival time of particles produced during proton-proton collisions. The HF Calorimeter is designed specifically to measure hadron particles, which are particles made up of quarks and gluons, in the forward region (i.e., close to the beamline) of the CMS detector. The HF Calorimeter is located at the very front and back of the CMS detector, at a distance of about 11.2 meters from the interaction point. This placement allows it to cover a pseudorapidity range of 2.9 to 5.2, which is important for measuring particles produced at small angles relative to the beamline. The HF Calorimeter is a sampling calorimeter, which means it consists of alternating layers of active and passive materials. The active material, in this case, is scintillating quartz fibers, which emit light when they interact with charged particles. The passive material is steel absorber plates, which serve to initiate hadron showers, causing the incident hadron to interact and create secondary particles. As these secondary particles pass through the scintillating fibers, they produce light, which is collected by photodetectors and converted into an electrical signal proportional to the particle's energy. Two separate algorithm are used for luminosity measurement in the HF Calorimeter, HFOC and HFET based on the Zero Counting (ZC) method and the Missing Transverse Energy (MET) methods respectively. %\cite{CMS-PAS-LUM-15-001}.

%The Zero Counting method is a threshold-based approach for estimating the luminosity. In this method, the total number of inelastic collisions, which produce new particles, is counted by measuring the energy deposited in the HF Calorimeter. To separate inelastic collisions from background noise and other processes, a threshold on the energy deposition is applied. During data-taking, the HF Calorimeter measures the energy deposited in each bunch crossing (when two bunches of protons pass through each other in the LHC). When the energy deposition in both HF Calorimeter sides (HF+ and HF-) is below a certain threshold, it is considered a "zero count" event, which means no inelastic collision has occurred. The number of zero count events is subtracted from the total number of bunch crossings, giving the number of inelastic collisions. The luminosity can then be calculated by dividing the number of inelastic collisions by the integrated time and the inelastic cross-section. The ZC method has the advantage of being robust against pile-up (simultaneous multiple proton-proton collisions) since it relies on counting the events where no energy is deposited. However, it may be affected by detector noise and other background processes that can lead to a non-zero energy deposition.
The zero counting method is used by particle colliders to measure the luminosity. In this method, the luminosity is estimated by counting the number of events with zero particles detected in a specific region of the detector. The basic idea behind the zero counting method is that the probability of having zero particles detected in a given region of the detector is proportional to the probability of having no collisions in that region. This probability can be related to the luminosity of the collisions through the following equation:

@@

where L is the luminosity, N is the number of events with zero particles detected in the region of interest, $N_0$ is the total number of events, $\sigma_{vis}$ is the visible cross-section. One advantage is that it is a simple and robust method that does not require sophisticated detectors or calibration procedures. However, it can be affected by background events, such as cosmic rays or beam-gas interactions, which can produce zero particles in the region of interest and increase the uncertainty in the luminosity measurement. \\
The Missing Energy method is an alternative approach for luminosity measurement in the HF Calorimeter. This method relies on measuring the total transverse energy (Et) deposited in the calorimeter and comparing it with the expected average transverse energy for inelastic collisions. The idea behind the MET method is that the total transverse energy should be conserved in a collision event. Inelastic collisions are expected to produce a certain amount of transverse energy on average, which can be estimated from simulations and theoretical calculations. The missing energy in an event is defined as the difference between the expected average transverse energy and the measured transverse energy in the HF Calorimeter. For each bunch crossing, the missing energy is calculated, and a distribution of missing energy values is obtained. This distribution is then fitted to a functional form, which includes a term for the inelastic collisions and terms for various background processes (e.g., detector noise, beam-gas interactions). The fit allows extracting the number of inelastic collisions, which can then be used to calculate the luminosity. The MET method is sensitive to the energy scale calibration of the detector and the modeling of background processes. However, it provides an independent and complementary measurement to the ZC method, which helps to reduce systematic uncertainties in the luminosity determination \cite{Sirunyan:2759951}.

@@

\item Muon drift tubes: The DT system is part of the CMS muon system, %which also includes the Resistive Plate Chambers (RPCs) and the Cathode Strip Chambers (CSCs).
  Drift Tubes (DTs) in the CMS experiment are designed to accurately measure the trajectory and momentum of muons produced in proton-proton collisions at the LHC.
  %The DT system is located in the barrel region of the CMS detector, covering the pseudorapidity range of $|\eta| < 1.2$.
  The DT system consist of rectangular drift cells filled with a gas mixture, typically of argon and carbon dioxide. The use of DT muon rates for luminosity measurement is based on the idea that the rate of single muon production is proportional to the instantaneous luminosity. Single muons comes from decay of inclusive, Z, W, top and jets.
%The DT system in the CMS detector is used for muon detection and precise position measurement. Drift Tubes are essentially gas-filled detectors. When muons pass through these tubes, they ionize the gas. The resulting ions and electrons drift under the influence of an electric field to anode wires located in the center of the tubes, producing a signal. By measuring the drift time, one can infer the position of the muon's trajectory.
To use the DT muon rates as a luminometer, one would need to count the rate of detected muons as a function of the delivered luminosity. However, the DT muon rate luminometer is not independently calibrated during the Van der Meer (vdM) scan due to low measured rate. It is cross calibrated with PCC or HF.

@@

\item Pixel Cluster Counting (PCC): The pixel detector in the CMS experiment is made up of multiple layers of silicon sensors arranged in a cylindrical shape around the beam pipe. When charged particles from the collisions pass through the silicon sensors, they create electric charge that is read out as a signal. The signals from adjacent sensors are combined to form clusters, which represent the position of the particle track in the detector. The total number of clusters detected over a certain period of time is used to estimate the luminosity. The PCC provides a precise measurement of the luminosity and is particularly useful when the collision rate is high \cite{CMS-PAS-LUM-13-001}.

@@

The pixel detector is one of the subdetectors of the CMS experiment that is closest to the interaction point where the proton beams collide. It consists of four barrel layers (L1-L4) at radii of 29, 68, 109 and 160 mm and three forward disks (D1-D3) on each end at distances of 291, 396, and 516 mm of pixel sensors from the center of the detector as shown in Fig.~\ref{fig:phaseI_upgrade}. It is built from 1856 silicon sensor modules, 1184 modules in the barrel layers (BPIX) and 672 modules for the forward disks (FPIX) \cite{Adam:2748381}. Modules for barrel layers and forward disks are shown in Fig.~\ref{fig:pixelmodule}. Table~\ref{tab:modpix} shows the number of modules in each pixel layer and disk. The modules in BPIX L1 are designed to handle high particle densities and radiation levels. Each module in this layer consists of a matrix of 4160 pixels, arranged in 160 rows and 26 columns. The pixel size in BPIX L1 is approximately 100x150 µm², which allows for high-resolution position measurements of charged particles. The modules in BPIX L2-4 layers are designed to withstand lower radiation levels compared to BPIX L1. Each module in BPIX L2-4 consists of a matrix of 66560 pixels, arranged in 260 rows and 256 columns. The pixel size in BPIX L2-4 is also approximately 100x150 µm². The FPIX modules are also designed to handle high particle densities and radiation levels. Each module in the FPIX consists of a matrix of 16128 pixels, arranged in 160 rows and 101 columns with same pixel size as layer pixels.
%It provide high-precision position measurements of the charged particles produced in the collisions. These position measurements are used to reconstruct the trajectories of the particles and to identify the particles themselves.
The pixel detector has a high position resolution, with a spatial resolution of 4.8  microns in the transverse direction and 7.99 microns in the longitudinal direction. The pixel detector also has a high time resolution, with a readout time of 25 nanoseconds. The pixel detector is capable of detecting charged particles with a wide range of energies, from a few hundred MeV to several TeV. The pixel detector is able to operate at very high particle fluxes, with a hit rate of up to $100 MHz/cm^2$. To achieve this high rate capability, the pixel detector uses fast readout electronics.
%which can read out the signals from the pixels in a few microseconds.
The pixel detector is also designed to operate at a high radiation level, with a dose of up to $5 \times 10^{14} neutrons/cm^2$ expected over the lifetime of the detector. To mitigate the effects of radiation damage, the pixel detector uses sensors made of high-purity silicon and a cooling system that keeps the detector at a temperature of -20°C. The pixel detector is  used as a primary luminometer. The luminosity measurement is based on counting the number of pixel clusters produced in the detector by the proton-proton collisions.  However, there are several challenges to accurately measure the luminosity with the pixel detector. One challange is the multiple proton-proton collisions per bunch crossing (pileup). Another challenge is the non-linearity of the pixel detector response, which can lead to inaccuracies in the luminosity measurement. Therefore, the motivation of this research work is to develop and test more precise techniques for measuring the luminosity with the pixel detector.

@@

The Pixel Cluster Counting (PCC) method is one of the main luminosity measurement technique used at the CMS experiment. The PCC method is based on counting the number of pixel clusters produced by the collisions in the CMS pixel detector, which is a high-resolution silicon detector located close to the collision point. The pixel detector is made up of more than 124 million pixels. The detector is designed to detect charged particles produced in the collisions, and the pixel clusters are formed when several neighboring pixels are hit by a single particle. The PCC method is based on the assumption that the number of pixel clusters produced is proportional to the number of collisions, and therefore to the luminosity. The proportionality constant is called the pixel detector visible cross section, and it can be determined with a calibration method described in section 3.1. The PCC method is implemented in two stages: the online and offline stages. In the online stage, the pixel clusters are counted in real time by the CMS data acquisition system, which uses a custom-designed ASIC chip to process the pixel detector signals. %The online luminosity measurement is therefore available within seconds of the collisions, and it is used to monitor the stability of the detector and to provide feedback to the LHC operators.
In the offline stage, the raw data from the pixel detector is analyzed using dedicated software to determine the pixel clusters and to calculate the luminosity. The offline luminosity measurement is more accurate than the online measurement, as it takes into account various corrections and calibrations that are not possible in real time. %The offline luminosity measurement is also used to determine the absolute luminosity scale, which is obtained from beam parameters.
There are several steps involved in the PCC method for measuring luminosity like data acquisition, pixel cluster reconstruction, pixel cluster counting as described below.

@@

\item Pixel cluster reconstruction is the process of identifying groups of adjacent pixels that have been fired by a single particle passing through the detector. The first step in the pixel cluster reconstruction process is to identify individual pixel hits in the data frames obtained from the pixel detector data acquisition system. A pixel hit is a small region of the pixel detector where charge has been deposited by a particle. The next step is to identify "seed" pixels, which are individual pixels with a high signal-to-noise ratio. A seed pixel is defined as a pixel hit with a signal above a certain threshold, which is typically set at a few times the noise level of the pixel detector. Once seed pixels have been identified, the next step is to build pixel clusters around each seed pixel. This is done by adding adjacent pixels with a signal above a lower threshold, called the cluster threshold. The cluster threshold is typically set at a level that minimizes the number of fake clusters while maximizing the efficiency of cluster finding. After pixel clusters have been built, the next step is to split or merge clusters as needed. This is done to remove fake clusters caused by noise or overlapping particles, and to merge clusters that are split due to inefficiencies in the cluster building process. Once the pixel clusters have been identified and merged/split as necessary, they are parameterized by their position and energy. The position of the cluster is determined by the center of gravity of the pixels in the cluster, and the energy is determined by summing the signal of all the pixels in the cluster. Finally, a set of selection criteria are applied to the pixel clusters to remove any remaining fake clusters and select only those clusters that are likely to be from real particle interactions. These selection criteria typically include requirements on the size, shape, and energy of the clusters.

\item The number of pixel clusters is counted over a fixed time intervals, known as lumi section. One lumi section is 23.36 seconds time interval. In the pixel cluster counting process, events of interest are selected from the large dataset obtained from the CMS experiment. This is typically done using zero bias triggers that select events that are coming from filled bunch crossing.
  %Once the events of interest have been selected, reconstruction the pixel clusters in each event is done using the steps described in the previous bullet point.
  %This involves identifying individual pixel hits, identifying seed pixels, building pixel clusters around each seed pixel, and parameterizing the clusters.
  After the pixel clusters have been reconstructed in each event, the next step is to count the number of clusters in each event. This can be done using simple counting algorithms that count the number of clusters above a certain energy threshold. %or more sophisticated algorithms that use machine learning techniques to identify and count clusters.
  The number of pixel clusters in each event is affected by various sources of background noise. %such as electronic noise and cosmic ray background.
  To accurately measure the number of signal clusters in each event, these background sources must be subtracted from the total cluster count.
 %This can be done using techniques such as sideband subtraction or template fitting. %Finally, to obtain an accurate measurement of the number of particles that passed through the pixel detector, the cluster counts must be corrected for the inefficiencies in the cluster reconstruction process. This can be done using simulation or other techniques to estimate the efficiency of the cluster finding algorithm as a function of the particle energy, position, and type.

@@

The PCC method has several advantages over the other luminosity measurement methods used by the CMS experiment. The PCC method is based on the pixel detector, which has a high spatial resolution and can accurately measure the position and energy of charged particles. Another advantage is its high precision and stability, as it is based on a well-understood physical process and has a small systematic uncertainty. %Another advantage is its independence from the beam conditions, as the pixel detector is insensitive to the beam halo and the beam-gas interactions.
The PCC method is also robust against pile-up, which is the presence of multiple proton-proton interactions in a single bunch crossing, as it can distinguish between pixel clusters produced by different collisions. %The PCC method is based on the pixel detector, which has a high spatial resolution and can accurately measure the position and energy of charged particles.
This allows for precise measurements of the luminosity, even when the particle collision rate is high. The pixel detector has a high detection efficiency, meaning that it can detect a large fraction of the particles produced in the collisions. The pixel detector's high granularity enables precise detection of individual particles. %The pixel cluster counting method is relatively insensitive to pileup, allowing accurate luminosity measurements even when pileup is high,
It has a wide dynamic range, capable of measuring luminosities from low to high due to the large number of pixels.

@@

The PCC method has been extensively tested and validated by the CMS during the LHC Run 1 and Run 2, which corresponded to proton-proton collisions at center-of-mass energies of 7-8 TeV and 13 TeV, respectively. The PCC method has achieved a relative luminosity precision of about 1.5 \%, which is well within the design goals of the CMS \cite{pas_18}. In the future, the PCC method will continue to be a key component of the CMS luminosity measurement strategy, as it provides a precise and robust measurement of the luminosity ratio between different datasets and periods. The PCC method will also benefit from the upgrades and improvements planned for the CMS pixel detector and the LHC, which will increase the luminosity and the collision rate, and will challenge the performance and the calibration of the PCC method. The CMS is planning to install a new pixel detector for the High-Luminosity LHC (HL-LHC) era, which will feature smaller pixel sizes, faster readout electronics, and radiation-hard materials. The CMS is also planning to develop new techniques and algorithms for the PCC method, such as machine learning methods, deep neural networks, and real-time analysis tools.

@@

>>>>

\item Fast Beam Conditions Monitor (BCM1F) : The BCM1F is specifically designed to detect the ionization produced by charged particles passing through its diamond sensors, and to convert this signal into a measurement of the beam intensity and luminosity. During Run 2, the BCM1F consisted of 24 diamond sensors, each with an active area of 1 cm², arranged in six rings around the beam pipe. The diamond sensors are positioned very close to the CMS detector, just 10 cm away from the beam pipe. This allows the sensors to detect the charged particles produced by the proton-proton collisions. When charged particles pass through the diamond sensors, they ionize the carbon atoms in the diamond crystal, producing electrons and holes. The electrons and holes are then collected by metal electrodes embedded in the diamond, producing a voltage signal proportional to the ionization produced by the charged particles. The voltage signal is then amplified by fast electronics and converted into a digital signal, which is sent to the CMS data acquisition system for further analysis. To measure the luminosity, the BCM1F counts the number of charged particles passing through each diamond sensor per unit time. The signal from each sensor is integrated over a short time interval (usually 25 ns), corresponding to the time it takes for a single proton bunch to pass through the sensors. The integrated signal is then converted into a measure of the instantaneous luminosity, which is proportional to the product of the number of charged particles per bunch and the collision frequency.

@@

\item Hadron Forward Calorimeter: The Hadron Forward (HF) Calorimeter is a critical component of the CMS experiment. It is a subdetector that measures the energy, position and arrival time of particles produced during proton-proton collisions. The HF Calorimeter is designed specifically to measure hadron particles, which are particles made up of quarks and gluons, in the forward region (i.e., close to the beamline) of the CMS detector. The HF Calorimeter is located at the very front and back of the CMS detector, at a distance of about 11.2 meters from the interaction point. This placement allows it to cover a pseudorapidity range of 2.9 to 5.2, which is important for measuring particles produced at small angles relative to the beamline. %The HF Calorimeter is a sampling calorimeter, which means it consists of alternating layers of active and passive materials.
The active material, in this case, is scintillating quartz fibers, which emit light when they interact with charged particles. The passive material is steel absorber plates, which serve to initiate hadron showers, causing the incident hadron to interact and create secondary particles. As these secondary particles pass through the scintillating fibers, they produce light, which is collected by photodetectors and converted into an electrical signal proportional to the particle's energy. Two separate algorithm are used for luminosity measurement in the HF Calorimeter, HFOC and HFET based on the Zero Counting (ZC) method and the sum of transverse energy methods respectively. %\cite{CMS-PAS-LUM-15-001}.

%The Zero Counting method is a threshold-based approach for estimating the luminosity. In this method, the total number of inelastic collisions, which produce new particles, is counted by measuring the energy deposited in the HF Calorimeter. To separate inelastic collisions from background noise and other processes, a threshold on the energy deposition is applied. During data-taking, the HF Calorimeter measures the energy deposited in each bunch crossing (when two bunches of protons pass through each other in the LHC). When the energy deposition in both HF Calorimeter sides (HF+ and HF-) is below a certain threshold, it is considered a "zero count" event, which means no inelastic collision has occurred. The number of zero count events is subtracted from the total number of bunch crossings, giving the number of inelastic collisions. The luminosity can then be calculated by dividing the number of inelastic collisions by the integrated time and the inelastic cross-section. The ZC method has the advantage of being robust against pile-up (simultaneous multiple proton-proton collisions) since it relies on counting the events where no energy is deposited. However, it may be affected by detector noise and other background processes that can lead to a non-zero energy deposition.
The zero counting method is used by particle colliders to measure the luminosity. In this method, the luminosity is estimated by counting the number of events with zero particles detected in a specific region of the detector. The basic idea behind the zero counting method is that the probability of having zero particles detected in a given region of the detector is proportional to the Poisson probability of having no collisions in that region. This probability can be related to the luminosity of the collisions through the following equation:

@@

where L is the luminosity, N is the number of events with zero particles detected in the region of interest, $N_0$ is the total number of events, $\sigma_{vis}$ is the visible cross-section. One advantage is that it is a simple and robust method that does not require sophisticated detectors or calibration procedures. However, it can be affected by background events, such as cosmic rays or beam-gas interactions. \\
The HFET algorithm measures luminosity by summing transverse energy deposits in the HF calorimeter cells. It relies on the direct proportionality between the total transverse energy and the particle flux from the interaction point. Accurate calibration of calorimeter cells is crucial for this method, as it ensures that the aggregate transverse energy accurately reflects the luminosity of the particle collisions \cite{Sirunyan:2759951.

%The Missing Energy method is an alternative approach for luminosity measurement in the HF Calorimeter. This method relies on measuring the total transverse energy (Et) deposited in the calorimeter and comparing it with the expected average transverse energy for inelastic collisions. The idea behind the MET method is that the total transverse energy should be conserved in a collision event. Inelastic collisions are expected to produce a certain amount of transverse energy on average, which can be estimated from simulations and theoretical calculations. The missing energy in an event is defined as the difference between the expected average transverse energy and the measured transverse energy in the HF Calorimeter. For each bunch crossing, the missing energy is calculated, and a distribution of missing energy values is obtained. This distribution is then fitted to a functional form, which includes a term for the inelastic collisions and terms for various background processes (e.g., detector noise, beam-gas interactions). The fit allows extracting the number of inelastic collisions, which can then be used to calculate the luminosity. The MET method is sensitive to the energy scale calibration of the detector and the modeling of background processes. However, it provides an independent and complementary measurement to the ZC method, which helps to reduce systematic uncertainties in the luminosity determination \cite{Sirunyan:2759951}.

@@

\item Muon drift tubes: The DT system is part of the CMS muon system, %which also includes the Resistive Plate Chambers (RPCs) and the Cathode Strip Chambers (CSCs).
  Drift Tubes (DTs) in the CMS experiment are designed to accurately measure the trajectory and momentum of muons produced in proton-proton collisions at the LHC.
  %The DT system is located in the barrel region of the CMS detector, covering the pseudorapidity range of $|\eta| < 1.2$.
  The DT system consist of rectangular drift cells filled with a gas mixture, typically of argon and carbon dioxide. The use of DT muon rates for luminosity measurement is based on the idea that the rate of single muon production is proportional to the instantaneous luminosity. Single muons comes from decay of inclusive, Z, W, top and jets.
%The DT system in the CMS detector is used for muon detection and precise position measurement. Drift Tubes are essentially gas-filled detectors. When muons pass through these tubes, they ionize the gas. The resulting ions and electrons drift under the influence of an electric field to anode wires located in the center of the tubes, producing a signal. By measuring the drift time, one can infer the position of the muon's trajectory.
  %To use the DT muon rates as a luminometer, one would need to count the rate of detected muons as a function of the delivered luminosity.
However, the DT muon rate luminometer is not independently calibrated during the van der Meer (vdM) scan due to low measured rate. It is cross calibrated with PCC or HF.

@@

\item Pixel Cluster Counting (PCC): The pixel detector in the CMS experiment is made up of multiple layers of silicon sensors arranged in a cylindrical shape around the beam pipe. When charged particles from the collisions pass through the silicon sensors, they create electric charge that is read out as a signal. The signals from adjacent pixels are combined to form clusters, which represent the position of the particle track in the detector. The total number of clusters detected over a certain period of time is used to estimate the luminosity. The PCC provides a precise measurement of the luminosity and is particularly useful when the collision rate is high \cite{CMS-PAS-LUM-13-001}.

@@

The pixel detector is one of the subdetectors of the CMS experiment that is closest to the interaction point where the proton beams collide. It consists of four barrel layers (L1-L4) at radii of 29, 68, 109 and 160 mm and three forward disks (D1-D3) on each end at distances of 291, 396, and 516 mm of pixel sensors from the center of the detector as shown in Fig.~\ref{fig:phaseI_upgrade}. It is built from 1856 silicon sensor modules, 1184 modules in the barrel layers (BPIX) and 672 modules for the forward disks (FPIX) \cite{Adam:2748381}. Modules for barrel layers and forward disks are shown in Fig.~\ref{fig:pixelmodule}. Table~\ref{tab:modpix} shows the number of modules in each pixel layer and disk. The modules in BPIX L1 are designed to handle high particle densities and radiation levels. Each module in this layer consists of a matrix of 4160 pixels, arranged in 160 rows and 26 columns. The pixel size in BPIX L1 is approximately 100x150 µm², which allows for high-resolution position measurements of charged particles. The modules in BPIX L2-4 layers are designed to withstand lower radiation levels compared to BPIX L1. Each module in BPIX L2-4 consists of a matrix of 66560 pixels, arranged in 260 rows and 256 columns. The pixel size in BPIX L2-4 is also approximately 100x150 µm². The FPIX modules are also designed to handle high particle densities and radiation levels. Each module in the FPIX consists of a matrix of 16128 pixels, arranged in 160 rows and 101 columns with same pixel size as layer pixels.
%It provide high-precision position measurements of the charged particles produced in the collisions. These position measurements are used to reconstruct the trajectories of the particles and to identify the particles themselves.
The pixel detector has a high position resolution, with a spatial resolution of 4.8  microns in the transverse direction and 7.99 microns in the longitudinal direction. The pixel detector also has a high time resolution, with a readout time of 25 nanoseconds. The pixel detector is capable of detecting charged particles with a wide range of energies, from a few hundred MeV to several TeV. The pixel detector is able to operate at very high particle fluxes, with a hit rate of up to $100 MHz/cm^2$. To achieve this high rate capability, the pixel detector uses fast readout electronics.
%which can read out the signals from the pixels in a few microseconds.
The pixel detector is also designed to operate at a high radiation level, with a dose of up to $5 \times 10^{14} neutrons/cm^2$ expected over the lifetime of the detector. To mitigate the effects of radiation damage, the pixel detector uses sensors made of high-purity silicon and a cooling system that keeps the detector at a temperature of -20°C. The pixel detector is  used as a primary luminometer. The luminosity measurement is based on counting the number of pixel clusters produced in the detector by the proton-proton collisions.  However, there are several challenges to accurately measure the luminosity with the pixel detector. One challange is the multiple proton-proton collisions per bunch crossing (pileup). Another challenge is the possible non-linearity or instabilities of the pixel detector response, which can lead to inaccuracies in the luminosity measurement. Therefore, the motivation of this research work is to develop and test more precise techniques for measuring the luminosity with the pixel detector.

@@

The Pixel Cluster Counting (PCC) method is one of the main luminosity measurement technique used at the CMS experiment. The PCC method is based on counting the number of pixel clusters produced by the collisions in the CMS pixel detector, which is a high-resolution silicon detector located close to the collision point. The pixel detector is made up of more than 124 million pixels. The detector is designed to detect charged particles produced in the collisions, and the pixel clusters are formed when several neighboring pixels are hit by a single particle. The PCC method is based on the assumption that the number of pixel clusters produced is proportional to the number of collisions, and therefore to the luminosity. The proportionality constant is called the pixel detector visible cross section, and it can be determined with a calibration method described in section 3.1. The PCC method exclusively utilizes offline luminosity measurement, comprising two stages: the "prompt-lumi," which is delayed by a few days and employs a non-optimized module list, and the "offline reprocessed luminosity" that uses an optimized module list for enhanced accuracy. During Run 2, the PCC online role was confined to recording pixel information, with cluster reconstruction occurring offline. However, in Run 3, this process evolved, allowing clusters to be reconstructed online within the High-Level Trigger (HLT) system, subsequently recorded for detailed offline analysis.
%The PCC method is implemented in two stages: the online and offline stages. In the online stage, the pixel clusters are counted in real time by the CMS data acquisition system, which uses a custom-designed ASIC chip to process the pixel detector signals. %The online luminosity measurement is therefore available within seconds of the collisions, and it is used to monitor the stability of the detector and to provide feedback to the LHC operators.
%In the offline stage, the raw data from the pixel detector is analyzed using dedicated software to determine the pixel clusters and to calculate the luminosity. The offline luminosity measurement is more accurate than the online measurement, as it takes into account various corrections and calibrations that are not possible in real time. %The offline luminosity measurement is also used to determine the absolute luminosity scale, which is obtained from beam parameters.
There are several steps involved in the PCC method for measuring luminosity like data acquisition, pixel cluster reconstruction, pixel cluster counting as described below.

@@

\item Pixel cluster reconstruction is the process of identifying groups of adjacent pixels that have been fired by a single particle passing through the detector. The first step in the pixel cluster reconstruction process is to identify individual pixel hits in the data frames obtained from the pixel detector data acquisition system. %A pixel hit is a small region of the pixel detector where charge has been deposited by a particle.
The next step is to identify "seed" pixels, which are individual pixels with a high signal-to-noise ratio. A seed pixel is defined as a pixel hit with a signal above a certain threshold, which is typically set at a few times the noise level of the pixel detector. Once seed pixels have been identified, the next step is to build pixel clusters around each seed pixel. This is done by adding adjacent pixels with a signal above a lower threshold, called the cluster threshold. The cluster threshold is typically set at a level that minimizes the number of fake clusters while maximizing the efficiency of cluster finding. After pixel clusters have been built, the next step is to split or merge clusters as needed. This is done to remove fake clusters caused by noise or overlapping particles, and to merge clusters that are split due to inefficiencies in the cluster building process. Once the pixel clusters have been identified and merged/split as necessary, they are parameterized by their position and energy. The position of the cluster is determined by the center of gravity of the pixels in the cluster, and the energy is determined by summing the signal of all the pixels in the cluster. Finally, a set of selection criteria are applied to the pixel clusters to remove any remaining fake clusters and select only those clusters that are likely to be from real particle interactions. These selection criteria typically include requirements on the size, shape, and energy of the clusters.

\item The number of pixel clusters is counted over a fixed time intervals, known as lumi section. One lumi section is 23.36 seconds time interval. In the pixel cluster counting process, events of interest are selected from the large dataset obtained from the CMS experiment. This is typically done using zero bias triggers that randomly select events that are coming from filled bunch crossing.
  %Once the events of interest have been selected, reconstruction the pixel clusters in each event is done using the steps described in the previous bullet point.
  %This involves identifying individual pixel hits, identifying seed pixels, building pixel clusters around each seed pixel, and parameterizing the clusters.
  After the pixel clusters have been reconstructed in each event, the next step is to count the number of clusters in each event. This can be done using simple counting algorithms that count the number of clusters above a certain energy threshold. %or more sophisticated algorithms that use machine learning techniques to identify and count clusters.

\item The number of pixel clusters in each event is affected by various sources of background noise. %such as electronic noise and cosmic ray background.
  To accurately measure the number of signal clusters in each event, these background sources must be subtracted from the total cluster count.
 %This can be done using techniques such as sideband subtraction or template fitting. %Finally, to obtain an accurate measurement of the number of particles that passed through the pixel detector, the cluster counts must be corrected for the inefficiencies in the cluster reconstruction process. This can be done using simulation or other techniques to estimate the efficiency of the cluster finding algorithm as a function of the particle energy, position, and type.

@@

The PCC method has several advantages over the other luminosity measurement methods used by the CMS experiment. The PCC method is based on the pixel detector, which has a high spatial resolution. Another advantage is its high precision and stability, as it is based on a well-understood physical process and has a small systematic uncertainty. %Another advantage is its independence from the beam conditions, as the pixel detector is insensitive to the beam halo and the beam-gas interactions.
The PCC method is also robust against pile-up, which is the presence of multiple proton-proton interactions in a single bunch crossing, as it can distinguish between pixel clusters produced by different collisions. %The PCC method is based on the pixel detector, which has a high spatial resolution and can accurately measure the position and energy of charged particles.
This allows for precise measurements of the luminosity, even when the particle collision rate is high. The pixel detector has a high detection efficiency, meaning that it can detect a large fraction of the particles produced in the collisions. The pixel detector's high granularity enables precise detection of individual particles. %The pixel cluster counting method is relatively insensitive to pileup, allowing accurate luminosity measurements even when pileup is high,
It has a wide dynamic range, capable of measuring luminosities from low to high due to the large number of pixels.

@@

%The PCC method has been extensively tested and validated by the CMS during the LHC Run 1 and Run 2, which corresponded to proton-proton collisions at center-of-mass energies of 7-8 TeV and 13 TeV, respectively. The PCC method has achieved a relative luminosity precision of about 1.5 \%, which is well within the design goals of the CMS \cite{pas_18}. In the future, the PCC method will continue to be a key component of the CMS luminosity measurement strategy, as it provides a precise and robust measurement of the luminosity ratio between different datasets and periods. The PCC method will also benefit from the upgrades and improvements planned for the CMS pixel detector and the LHC, which will increase the luminosity and the collision rate, and will challenge the performance and the calibration of the PCC method. The CMS is planning to install a new pixel detector for the High-Luminosity LHC (HL-LHC) era, which will feature smaller pixel sizes, faster readout electronics, and radiation-hard materials. The CMS is also planning to develop new techniques and algorithms for the PCC method, such as machine learning methods, deep neural networks, and real-time analysis tools.

@@

The PCC method has been extensively tested and validated by the CMS during the LHC Run 1 and Run 2, which corresponded to proton-proton collisions at center-of-mass energies of 7-8 TeV and 13 TeV, respectively. The PCC method has achieved a relative luminosity precision of about 1.5 \%, which is well within the design goals of the CMS \cite{pas_18}. In the future, the PCC method willcontinue to be a key component of the CMS luminosity measurement strategy, as it provides a precise and robust measurement of the luminosity ratio between different datasets and periods. The P\
CC method will also benefit from the upgrades and improvements planned for the CMS pixel detector and the LHC, which will increase the luminosity and the collision rate, and will challenge the performance and the calibration of the PCC method. The CMS is planning to install a new pixel detector for the High-Luminosity LHC (HL-LHC) era, which will feature smaller pixel sizes, faster readout electronics, and radiation-hard materials. The CMS is also planning to develop new techniques and algorithms for the PCC method, such as machine learning methods, deep neural networks, and real-time analysis tools.
